### 2019-10-08 thesis/txt/1-related-work.tex

\section{Build log analysis and augmentation}
Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs. They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

@@

\section{Production Log analysis}
\mention{logpai and drain}

@@

\section{Information extraction and retrieval techniques}
\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}. For our use case, this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}

>>>>

\section{Build Log Analysis and Augmentation}
Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs. They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

@@

\section{Production Log Analysis}
\mention{logpai and drain}

@@

\section{Information Extraction and Retrieval Techniques}
\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}. For our use case, this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}

### 2019-10-08 thesis/txt/3-data-set.tex

\section{Labeling (better name?)}
For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

    \paragraph{Description}
    learning steps combining keywords -> similar to how devs would learn from reading those models

@@

\section{Validation of our data set}
\todo{copy over from md doc}

\subsection{Inter-Rater Reliability}

\subsection{Sending Mails out to developers}

>>>>

\section{Labeling}
For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

    \paragraph{Description}
    for simple keyword search - imitate what users would search for ad-hoc

    learning steps combining keywords -> similar to how devs would learn from reading those models

@@

\section{Validation}
\todo{copy over from md doc}

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa

\subsection{Sending Mails to Developers}
study description \& results

### 2019-10-08 thesis/txt/4-tool.tex

\chapter{Information Extraction Techniques}
overview introduction text
\label{models}

\section{Our Model for IE Techniques}
\section{Our Model for extraction tasks}
\section{Our Model for extractable information}

\section{PROSE Program Synthesis}

\section{IR Similarity}

\section{Keyword search}

\section{further thechniques}

>>>>

\chapter{Our Information Extraction Tool}
\label{implementation}
describe implemantation of Tool
\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

\section{Common Interface} 
unification tool, reference CLI somehow nicely?,

ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)

\section{PROSE Program Synthesis}
implementation details :)

C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

\section{IR Similarity}
impl details,

R, text2vec, tokenized vectors, impl of preprocessing?

don't repeat from IE models section!

\section{Keyword search}
impl details,

R, simple!
